paper1_results_figs_slimmed_50_rr

### 2016-10-18 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
adding figs for final submission

## Figures for paper 1 : version 8

@@

@@

@@

## Fig. x1 Time-to-resistance across all input values

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=4.5}

@@

## Fig x2 PRCC analysis for time-to-resistance 0.5 for sequential and mixture strategies

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8}

@@

## Fig. x3 How time-to-resistance is effected by input values for each insecticide use strategy

@@

```{r, eval=TRUE, echo=FALSE, fig.height=2.5}

@@

  #for(i in names_inputs)
  for(i in in_cols)
    {

@@

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) +

             #ideally would include points but they obscure means
             #geom_point(shape=1, size=1, alpha=0.2, show.legend=FALSE) + 
             geom_smooth(linetype='dashed',size=0.5) +
             #facet_wrap( ~ strategy) +
             #labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #trying to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

           )
  }

@@

## Fig. x4 PRCC difference in time-to-resistance 0.5 between sequential and adaptive mixture strategies

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=5.5}

@@

## Fig. x5 Effectiveness and exposure together determine most of whether resistance arises slower under adaptive mixture or sequential strategies
1. Exposure and effectiveness can be used to predict most of whether resistance will arise slower under the sequential or adaptive mixture strategy, either by a simple plot or using classification trees.
```{r, eval=TRUE, echo=FALSE, fig.height=6}

@@

## Fig. x6 Modifying previous plot to show where resistance arises over 20% slower for adaptive mixture versus sequential.

1. The line fitted to runs where resistance is reached at the same time for mixture and sequential is retained. Less of the parameter space favours the adaptive mixture under these constraints.
```{r, eval=TRUE, echo=FALSE, fig.height=6}

@@

## Fig. x5.1 modified for mix2 vs seq

fewer runs where sequential gives slower resistance

```{r, eval=TRUE, echo=FALSE, fig.height=6}

  ggSubset <- dif_mix2_seq
  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mix2_better_seq0.5 <- ifelse( ggSubset$mix2_minus_seq0.5 > 0, 1, 0 )
  ggSubset$seq_better_mix20.5 <- ifelse( ggSubset$mix2_minus_seq0.5 < 0, 1, 0 )
  ggSubset$abs_diff <- abs(ggSubset$mix2_minus_seq0.5)

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$abs_diff==0),]
  #set these to 1 (they were 0)
  df_same$mix2_better_seq0.5 <- 1
  df_same$seq_better_mix20.5 <- 1
  #rbind them back onto other dataset
  ggSubset <- rbind( ggSubset, df_same)

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mix2_not20pc_better_seq0.5 <- ifelse( ggSubset$mix2_minus_seq0.5 / ggSubset$gen_cP0.5seq <= 0.2, 1, 0 )

    #find unequal runs
    unequal <- ggSubset[ggSubset$resist_start_lo_div_hi < 0.01,]
    #nrow(ggSubset)
    #nrow(unequal)
    #2721 out of the 6189 remaining runs

    #in how many runs was seq better than mix
    #sum(unequal$seq_better_mix20.5)
    #311

    library(viridis)

    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_diff))+

             facet_grid( ~ seq_better_mix20.5, labeller=as_labeller( c('0'='mixture\ntime to resistance\nlonger','1'='sequential\ntime to resistance\nlonger'))) +

             #now add the unequal points
             #showed that they were on both sides
             #geom_point(data = unequal, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='red', shape=2) +

  l_mod <- lm(y1 ~ x1)
  #l_mod$coefficients
  #(Intercept)          x1 
  #1.019330    0.560508

## Fig. x7 Classification Trees for whether resistance arises slower with an adaptive mixture or sequential strategy. The upper plot shows when mixture is slower than sequential, the lower plot is for when the mixture is more than 20% slower.

```{r, eval=TRUE, echo=FALSE, warning=TRUE, message=FALSE, fig.height=3.5}

  #code copied from sensiAnPaper1All

@@

  #just doing for a few strategies, sensiAnPpaer1All.Rmd does for a bunch
  # treeResponses <- c( rownames(resistBetterMix_ASeq)[2], #2 is 25%
  #                     rownames(resistBetterMix_ASeq20)[2]
  #                   )
  #4/7/16 eek above before was a bug showing 25% rather than 50%
  treeResponses <- c( "betterMix_ASeq_cP0.5","betterMix_ASeq20_cP0.5")

  #to do trees & plots for all response variables
  for( treeResponse in treeResponses )
  {
    tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
    #http://stackoverflow.com/questions/29197213/what-is-the-difference-between-rel-error-and-x-error-in-a-rpart-decision-tree
    #A rule of thumb is to choose the lowest level where the rel_error + xstd < xerror.

    cpOptimal <- tree$cptable[ tree$cptable[,"rel error"] + tree$cptable[,"xstd"]  < tree$cptable[,"xerror"],"CP"][1]
    treePruned <- prune(tree, cp=cpOptimal)

    #test tree pruning, seemed to suggest we are pruning more than needed
    # plotcp(tree)  
    # 
    # cat("optimal cp used in pruning=",cpOptimal,"\n")

    #to set box colours
    cols <- ifelse(treePruned$frame$yval == 1, "red", "green3")

    #adds in no. scenarios correctly and incorrectly classified
    #prp(tree, extra=1, varlen = 10, main=treeResponse)
    #prp(treePruned, extra=1, varlen = 10, main=treeResponse, col=cols, border.col=cols)
    #prp(treePruned, extra=1, varlen = 0, main=treeResponse, box.col=cols, under=TRUE)
    prp(treePruned, extra=1, varlen = 0, main=main, box.col=cols, under=TRUE)
  }

  #4/7/2016 testing the unpruned trees, repeats previous loop with pruning removed
  for( treeResponse in treeResponses )
  {
    tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class')

@@

    #adds in no. scenarios correctly and incorrectly classified
    prp(tree, extra=1, varlen = 0, main=main, box.col=cols, under=TRUE)
  }

@@

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5} 
#eval=FALSE so this one not displayed

## Fig. x8 Introducing a new insecticide when there is already resistance to an existing one. This takes Curtis Fig 2 and sets the starting frequency for each allele in turn to a higher level to represent an 'old' insecticide to which there is resistance. In both cases resistance to the new insecticide develops slower when the 'old' insecticide continues to be used (mixture) than when it doesn't (sequence).

#curtis_f2 with P_1 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.49 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , rr_restoration_ins1=0.23/0.73, rr_restoration_ins2 = 0.43/1, addCombinedStrategy=FALSE )

#curtis_f2 with P_2 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.01 , P_2 = 0.49 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , rr_restoration_ins1=0.23/0.73, rr_restoration_ins2 = 0.43/1, addCombinedStrategy=FALSE )

## Fig. x12 How sequential can be better than mixture. When the time taken for resistance to the first insecticide to be reached is greater than the difference in time taken for the second resistance to be reached in the presence and absence of the first insecticide.

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5}

>>>>

## Figures for paper 1 : version 9 : looking at producing Tiffs for submission

@@

```{r,include=FALSE}

library(knitr)

# options to create final publication quality figures
# causes the pdf document to fail, but the figs do get stored in pap1figs/
opts_chunk$set(dev="tiff",
               dev.args=list(compression="lzw"),
               dpi=300,
               cache=FALSE,
               fig.path='pap1figs/')
# opts_chunk$set(dev='postscript')
```

@@

#Fig1 
```{r Fig1, eval=TRUE, echo=FALSE, fig.height=7.5, fig.width=5, fig.show='hold', fig.align='left'}

library(ggplot2)
library(cowplot)

#Fig 1A

dfd1 <- selection_simple( freq=0.01, selection_co = 1, dominance = 1, num_gens = 150, plot=FALSE)
dfd05 <- selection_simple( freq=0.01, selection_co = 1, dominance = 0.5, num_gens = 150, plot=FALSE)
dfd0 <- selection_simple( freq=0.01, selection_co = 1, dominance = 0, num_gens = 150, plot=FALSE)

df_to_plot <- rbind(dfd1, dfd05, dfd0)

#old way of getting in wide format  
# df_to_plot <- data.frame(generation=dfd1$generation,
#                          dominance1=dfd1$freq,
#                          dominance0.5=dfd05$freq,
#                          dominance0=dfd0$freq)

plotlist[[1]] <- ggplot(df_to_plot, aes(x=generation, y=freq, 
                              colour=factor(dominance,labels=c("0   recessive",
                                                               "0.5 partial",
                                                               "1   dominant")))) + 
       theme_bw() +  
       #theme(legend.position = "bottom", legend.key = element_blank()) + 
       #guides(colour = guide_legend(reverse=TRUE)) +  
       labs(colour = "dominance") +
       ylab("Resistance Allele Frequency") +   
       #coord_trans(y = "log10") +    
       geom_line()

#Fig 1B

df_labs <- data.frame(lab=rep(c('RR','RS','SS'),4),
                      x=c(10,10,10,30,30,30,50,50,50,70,70,70),
                      y=c(50,46,42,38,34,30,26,22,18,14,10,6),
                      #col=c(2,1,1,2,1.5,1,2,2,1,2,2,2))
                      col=c(1,0,0,1,0.5,0,1,1,0,1,1,1))

df_boxes <- data.frame(lab=c('R recessive\n(slow spread)',
                             'R semi-dominant\n(rapid spread)',
                             'R dominant\n(rapid spread)',
                             'No selection for R'),
                      x=c(10,30,50,80),
                      y=c(90,75,60,35))

plotlist[[2]] <- ggplot(data.frame(x=c(0,100),y=c(80,0)), aes(x=x, y=y)) + 
       theme_bw() + 
       ylim(0,100) +   
       ylab("Insecticide concentration") +
       xlab("Time since treatment") +         
       geom_line(size=2, colour=rgb(0.5,0,0.5)) +
       geom_vline(xintercept = c(20,40,60), linetype=2) +
       geom_text(data=df_labs,aes(x=x, y=y, label=lab, colour=factor(col)),size=4) +
       scale_colour_manual(values = c("0" = "red","0.5" = "orange","1" = "green"), guide=FALSE) +  
       geom_label(data=df_boxes,aes(x=x, y=y, label=lab)) +
       theme(axis.text = element_blank(),
             axis.ticks = element_blank(),
             panel.grid = element_blank())

plot_grid( plotlist[[1]],plotlist[[2]],ncol=1, rel_heights=c(0.7,1))

# Fig2 replicating Curtis
```{r Fig2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, fig.keep='last'}

  #Beths code for these figures taken from resistanceMaster

  #set layout for 2 plots
  layout(t(1:2))

  #2A
  calibration <- 1011
  input <- createInputMatrix( params.csv=FALSE, calibration=calibration )
  listOut <- runModel2( input, calibration )
  #we submitted the LD one but should have done the Fig1
  #plotcurtis_ld( listOut$results[[1]], listOut$results[[2]], 1, 4 )
  plotcurtis_f1( listOut$results[[1]], listOut$results[[2]], 1, 2 )

  #2B
  calibration <- 1012
  input <- createInputMatrix( params.csv=FALSE, calibration=calibration )
  listOut <- runModel2( input, calibration )  
  plotcurtis_f2( listOut$results[[3]], listOut$results[[1]], listOut$results[[2]], 1, 2, 3 )

@@

## Fig 3

```{r Fig3, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=4.5}

#get input values from Ian, then I can re-generate, might want to change mix2 to mix
#90% exposure, equal for female and male
#Starting freq. at locus A =0.01 and at locus B is 0.001
#Fitness =1 for RR genotypes at 0 for SR and SS at both loci

runcurtis_f2( P_1 = 0.01 , P_2 = 0.001, h.RS1_A0 = 1, h.RS2_0B = 1, exposure = 0.9,                        phi.SS1_A0 = 1 , phi.SS2_0B = 1 , s.RR1_A0 = 1 , s.RR2_0B = 1,
              addCombinedStrategy=FALSE, addStrategyLabels=FALSE )

## Fig4 Time-to-resistance across all input values

@@

```{r Fig4, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=4.5}

@@

## Fig5 PRCC analysis for time-to-resistance 0.5 for sequential and mixture strategies

@@

```{r Fig5, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8}

@@

## Fig6 How time-to-resistance is effected by input values for each insecticide use strategy

@@

```{r Fig6, eval=TRUE, echo=FALSE, fig.height=7.5, fig.keep='last'}

  #layout for 3 panel plot (t=horiz, c=vertical)
  #doesn't work for ggplot
  #layout(c(1:3))

  #list to put plots in for cowplot
  plotlist <- list(3)

@@

  #for(i in names_inputs)

  plotnum <- 0

  for(i in in_cols)
    {

@@

    plotnum <- plotnum + 1

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    plotlist[[plotnum]] <- ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) +

             #ideally would include points but they obscure means
             #geom_point(shape=1, size=1, alpha=0.2, show.legend=FALSE) + 
             geom_smooth(linetype='dashed',size=0.5) +
             #facet_wrap( ~ strategy) +
             #labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #trying to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_label(data = curtisInputs, inherit.aes=FALSE, aes_string(x=i, y=210, label='"Curtis\nFig.2"'), size=3, colour='red', nudge_x = -0.05)

  }

  plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1))

@@

## Fig7 PRCC difference in time-to-resistance 0.5 between sequential and adaptive mixture strategies

@@

```{r Fig7, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=5.5}

@@

## Fig9 Effectiveness and exposure together determine most of whether resistance arises slower under adaptive mixture or sequential strategies
1. Exposure and effectiveness can be used to predict most of whether resistance will arise slower under the sequential or adaptive mixture strategy, either by a simple plot or using classification trees.
```{r Fig9, eval=TRUE, echo=FALSE, fig.height=6}

@@

## Fig10 Modifying previous plot to show where resistance arises over 20% slower for adaptive mixture versus sequential.

1. The line fitted to runs where resistance is reached at the same time for mixture and sequential is retained. Less of the parameter space favours the adaptive mixture under these constraints.
```{r Fig10, eval=TRUE, echo=FALSE, fig.height=6}

@@

## Fig8 Classification Trees for whether resistance arises slower with an adaptive mixture or sequential strategy. The upper plot shows when mixture is slower than sequential, the lower plot is for when the mixture is more than 20% slower.

```{r Fig8, eval=TRUE, echo=FALSE, warning=TRUE, message=FALSE, fig.height=7, fig.keep='last'}

  #layout for 2 panel plot (t=horiz, c=vertical)
  layout(c(1:2))

@@

  treeResponses <- c( "betterMix_ASeq_cP0.5","betterMix_ASeq20_cP0.5")

  #pruned trees commented out, not used in paper1
  # for( treeResponse in treeResponses )
  # {
  #   tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
  #   #http://stackoverflow.com/questions/29197213/what-is-the-difference-between-rel-error-and-x-error-in-a-rpart-decision-tree
  #   #A rule of thumb is to choose the lowest level where the rel_error + xstd < xerror.
  #   
  #   cpOptimal <- tree$cptable[ tree$cptable[,"rel error"] + tree$cptable[,"xstd"]  < tree$cptable[,"xerror"],"CP"][1]
  #   treePruned <- prune(tree, cp=cpOptimal)
  #   
  #   #test tree pruning, seemed to suggest we are pruning more than needed
  #   # plotcp(tree)  
  #   # cat("optimal cp used in pruning=",cpOptimal,"\n")
  #   
  #   #to set box colours
  #   cols <- ifelse(treePruned$frame$yval == 1, "red", "green3")
  #   
  #   #add fig label
  #   if (treeResponse == treeResponses[1]) main <- "A)" 
  #   else  main <- "B)"
  # 
  #   #adds in no. scenarios correctly and incorrectly classified
  #   prp(treePruned, extra=1, varlen = 0, main=main, box.col=cols, under=TRUE)
  # }

  #4/7/2016 unpruned trees, repeats previous loop with pruning removed
  for( treeResponse in treeResponses )
  {
    tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class')

@@

    #adds in no. scenarios correctly and incorrectly classified
    #cex to set textsize (0.7 all text doesn't quite fit in), good that A&B are now same size
    #round=0 to make boxes square
    #split.font=1 to stop bold text in labels
    prp(tree, extra=1, varlen = 0, main=main, box.col=cols, under=TRUE, 
        cex=0.4, round=0, split.font=1, ycompress = TRUE )
  }

@@

## Fig11  How sequential can be better than mixture. When the time taken for resistance to the first insecticide to be reached is greater than the difference in time taken for the second resistance to be reached in the presence and absence of the first insecticide.

```{r Fig11, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5}
